---
title: "SAL 413 HW5"
author: "Hunter Geise"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
This homework will work on data manipulation primarily using dplyr and lubridate, but other tidyverse packages may also be used. Do not use any Base R functions to work with any Date data. Only rely on lubridate functions (lubridate has the function as_date() if needed). Each question will build on the results from the previous question. Read each question carefully as steps to solving the question may be laid out in the question itself.
Download the Fixed_CFB_Scores_21.csv file from Blackboard (this is a sizeable file and may take time to download and/or load into your R session).
```{r, message=FALSE}
library(tidyverse)
library(dplyr)
library(lubridate)
theme_set(theme_bw())

data <- read_csv("cfb_scores.csv")

data %>%
  select(-c(2, 3, 4, 8, 10, 11, 17, 18, 19, 20, 
            21, 22, 23, 24, 25, 26, 27, 28, 29, 
            30, 31, 32, 36, 37, 38, 39, 40, 41, 
            42, 43, 44, 47, 48, 49, 50, 51, 52, 
            53, 54, 55, 56, 57, 58, 59)) -> data
```
\newpage

1. Using lubridate and other tidyverse packages, create a logical variable in the data that determines if each observation occurred between 12/17/21 and 1/4/22 (these are the dates bowl games were played). Then limit the data to only contain observations where this variable is true.
```{r}
data %>%
  mutate(is_bowl_game = as.Date(wallclock) %within%
           (ymd("21/12/17") %--% ymd("22-1-5"))) -> data

data %>%
  filter(is_bowl_game == TRUE) -> bowl_game

bowl_game %>%
  select(c(game_id, homeScore, awayScore, wallclock, 
           type.text, is_bowl_game)) -> new_bowl_game

new_bowl_game
```
\newpage

2. For each game in the data, find whether the “home” team won the game by checking the final scores for each game. What proportion of bowl games did the “home” team win?
```{r, message=FALSE}
new_bowl_game %>%
  filter(type.text == "End of Game") -> game_over

game_over %>%
  summarise(home_win = homeScore > awayScore) -> hw

mean(hw$home_win)
```
\newpage

3. Create a dataset with variables game_id, home_team, away_team, and total_points that lists the total points scored in the two bowl games with the most combined points scored by the two teams and the fewest points scored. The end result will have 4 columns and just 2 rows: 1 row for the game with the most points scored and 1 row for the game with the fewest points scored.
```{r}
bowl_game %>% 
  filter(type.text == "End of Game") %>%
  mutate(total_points = awayScore + homeScore) -> points

points %>%
  select(c(game_id, home_team, away_team, total_points)) %>%
  tibble() -> points

points %>%
  arrange(total_points) -> lowest_pts

lowest_pts %>% slice(1) -> lowest_pts

points %>%
  arrange(desc(total_points)) -> highest_pts

highest_pts %>% slice(1) -> highest_pts

final_points_table <- bind_rows(highest_pts, lowest_pts)

final_points_table
```
\newpage


