---
title: "lottery pick"
author: "Hunter Geise"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(nbastatR)
library(dplyr)
library(openxlsx)
library(randomForest)
library(modelr)
library(DescTools)
library(vip)
Sys.setenv(VROOM_CONNECTION_SIZE = "300000")
```

#Scraping and Cleaning Data#
```{r}
data <- drafts(draft_years = 2000:2016)
lottery_picks <- data %>% 
  filter(numberPickOverall <= 14) %>%
  select(yearDraft, numberPickOverall, namePlayer,
         idPlayer, nameTeam)

bref_data <- players_careers(players = lottery_picks$namePlayer, 
                             modes = "Totals",
                             add_mode_names = TRUE)
```

#Merging data#
```{r}
merged_data <- merge(lottery_picks, dataPlayerCareerTotalsRegularSeason, by = "namePlayer")
merged_data <- merged_data %>%
  select(-c(idTeam, idPlayer.x, slugSeasonType, urlNBAAPI, idPlayer.y, nameTeam))
  
merged_data <- merged_data %>%
  arrange(yearDraft, numberPickOverall)

write.xlsx(merged_data, file = "mock_comp.xlsx")

updated_data <- read.csv("mock_comp.csv")

updated_data <- updated_data %>%
  select(-c(pctFG, pctFG3, pctFT, pctFG2, trebTotals, fgmTotals, fgaTotals))
```

#Random forest to create weights#
```{r}
rf_data <- updated_data %>%
  select(-namePlayer)
#splitting the data
ind <- sample(1:nrow(rf_data), nrow(rf_data) * .7, replace = TRUE)
train_data <- rf_data[ind, ]
test_data <- rf_data[-ind, ]

#optimiziing minimum node size
find_nodes1 <- function(node) {
  mod1 <- randomForest(
    WS ~ yearDraft + numberPickOverall + gp + gs + fg3mTotals + fg3aTotals + 
      fg2mTotals + fg2aTotals + minutesTotals + ftmTotals + ftaTotals + orebTotals +
      drebTotals + astTotals + stlTotals + blkTotals + tovTotals + pfTotals + ptsTotals + 
      allStar + allNBA + Champion, 
    data = train_data,
    nodesize = ceiling(node)
  )
  rmse(mod1, test_data)
}

min_node1 <- optimize(find_nodes1, c(1,14))
print(min_node1)

#optimizing tree number
find_trees1 <- function(trees) {
  mod2 <- randomForest(
    WS ~ yearDraft + numberPickOverall + gp + gs + fg3mTotals + fg3aTotals + 
      fg2mTotals + fg2aTotals + minutesTotals + ftmTotals + ftaTotals + orebTotals +
      drebTotals + astTotals + stlTotals + blkTotals + tovTotals + pfTotals + ptsTotals + 
      allStar + allNBA + Champion,
    data = train_data,
    ntree = ceiling(trees)
  )
  rmse(mod2, test_data)
}

opt_tree1 <- optimize(find_trees1, c(5,100))
print(opt_tree1)

#Final Models With Random Forest Params
final_model1 <- randomForest(WS ~ yearDraft + numberPickOverall + gp + gs + fg3mTotals + fg3aTotals + 
                               fg2mTotals + fg2aTotals + minutesTotals + ftmTotals + ftaTotals + orebTotals +
                               drebTotals + astTotals + stlTotals + blkTotals + tovTotals + pfTotals + ptsTotals + 
                               allStar + allNBA + Champion,
                             data = rf_data,
                             ntree = opt_tree1$minimum,
                             nodesize = min_node1$minimum)

rf_importance <- importance(final_model1)
full_vip <- vip(final_model1)

full_vip +
  labs(title = "Importance of Career Stats on Win Shares",
       x = "Random Forest Variables") +
  theme(plot.title = element_text(hjust = 0.30)) +
  scale_x_discrete(labels = c(gs = "Games Started", 
                              ftaTotals = "Total Free Throws Attempted", 
                              minutesTotals = "Total Minutes Played",
                              ftmTotals = "Total Free Throws Made", 
                              ptsTotals = "Total Points", 
                              drebTotals = "Total Defensive Rebounds",
                              fg2aTotals = "Total 2Pt FG Attempted", 
                              fg2mTotals = "Total 2Pt FG Made", 
                              tovTotals = "Total Turnovers",
                              stlTotals = "Total Steals")) +
  theme(plot.background = element_rect(fill = "lightgray"))
```

#Creating weights and applying to data set#
```{r}
weights <- importance(final_model1)
normalized_weights <- weights/ sum(weights)

final_data <- read.csv("mock_comp_w_totals.csv")

final_data <- final_data %>% 
  select(-c(pctFG, pctFG3, pctFT, pctFG2, trebTotals, fgmTotals, fgaTotals))

final_data %>% 
  mutate(player_score = ((yearDraft * normalized_weights[1]) +
           (numberPickOverall * normalized_weights[2]) +
           (gp * normalized_weights[3]) +
           (gs * normalized_weights[4]) +
           (fg3mTotals * normalized_weights[5]) +
           (fg3aTotals * normalized_weights[6]) +
           (fg2mTotals * normalized_weights[7]) +
           (fg2aTotals * normalized_weights[8]) +
           (minutesTotals * normalized_weights[9]) +
           (ftmTotals * normalized_weights[10]) +
           (ftaTotals * normalized_weights[11]) +
           (orebTotals * normalized_weights[12]) +
           (drebTotals * normalized_weights[13]) +
           (astTotals * normalized_weights[14]) +
           (stlTotals * normalized_weights[15]) +
           (blkTotals * normalized_weights[16]) -
           (tovTotals * normalized_weights[17]) -
           (pfTotals * normalized_weights[18]) +
           (ptsTotals * normalized_weights[19]) +
           (allStar * normalized_weights[20]) +
           (allNBA * normalized_weights[21]) +
           (Champion * normalized_weights[22]))) -> final_data
```

#Original creation of quartiles and grading
```{r}
column_to_split <- final_data$player_score

quartiles <- quantile(column_to_split, probs = seq(0, 1, by = 1/5))

quartile_labels <- cut(column_to_split, breaks = quartiles, labels = FALSE, include.lowest = TRUE)

quartile_data <- final_data %>%
  select(c(namePlayer, yearDraft, numberPickOverall, player_score))

quartile_data$quartile <- quartile_labels

#Assigning grades to quartiles
quartile_data %>%
  mutate(grade = case_when(
    quartile == 5 ~ "A",
    quartile == 4 ~ "B",
    quartile == 3 ~ "C",
    quartile == 2 ~ "D",
    quartile == 1 ~ "F",
  )) -> quartile_data

```

#2000 grading
```{r}
data_2000 <- final_data %>%
  filter(yearDraft == 2000)

column_to_split <- data_2000$player_score

quartiles <- quantile(column_to_split, probs = seq(0, 1, by = 1/12))

quartile_labels <- cut(column_to_split, breaks = quartiles, labels = FALSE, include.lowest = TRUE)

quartile_data <- data_2000 %>%
  select(c(namePlayer, yearDraft, numberPickOverall, player_score))

quartile_data$quartile <- quartile_labels

#Assigning grades to quartiles
quartile_data %>%
  mutate(grade = case_when(
    quartile == 12 ~ "A",
    quartile == 11 ~ "A-",
    quartile == 10 ~ "B+",
    quartile == 9 ~ "B",
    quartile == 8 ~ "B-",
    quartile == 7 ~ "C+",
    quartile == 6 ~ "C",
    quartile == 5 ~ "C-",
    quartile == 4 ~ "D+",
    quartile == 3 ~ "D",
    quartile == 2 ~ "D-",
    quartile == 1 ~ "F",
  )) -> quartile_data_2000
```

#2001 grading
```{r}
data_2001 <- final_data %>%
  filter(yearDraft == 2001)

column_to_split <- data_2001$player_score

quartiles <- quantile(column_to_split, probs = seq(0, 1, by = 1/12))

quartile_labels <- cut(column_to_split, breaks = quartiles, labels = FALSE, include.lowest = TRUE)

quartile_data <- data_2001 %>%
  select(c(namePlayer, yearDraft, numberPickOverall, player_score))

quartile_data$quartile <- quartile_labels

#Assigning grades to quartiles
quartile_data %>%
  mutate(grade = case_when(
    quartile == 12 ~ "A",
    quartile == 11 ~ "A-",
    quartile == 10 ~ "B+",
    quartile == 9 ~ "B",
    quartile == 8 ~ "B-",
    quartile == 7 ~ "C+",
    quartile == 6 ~ "C",
    quartile == 5 ~ "C-",
    quartile == 4 ~ "D+",
    quartile == 3 ~ "D",
    quartile == 2 ~ "D-",
    quartile == 1 ~ "F",
  )) -> quartile_data_2001
```

#2002 grading
```{r}
data_2002 <- final_data %>%
  filter(yearDraft == 2002)

column_to_split <- data_2002$player_score

quartiles <- quantile(column_to_split, probs = seq(0, 1, by = 1/12))

quartile_labels <- cut(column_to_split, breaks = quartiles, labels = FALSE, include.lowest = TRUE)

quartile_data <- data_2002 %>%
  select(c(namePlayer, yearDraft, numberPickOverall, player_score))

quartile_data$quartile <- quartile_labels

#Assigning grades to quartiles
quartile_data %>%
  mutate(grade = case_when(
    quartile == 12 ~ "A",
    quartile == 11 ~ "A-",
    quartile == 10 ~ "B+",
    quartile == 9 ~ "B",
    quartile == 8 ~ "B-",
    quartile == 7 ~ "C+",
    quartile == 6 ~ "C",
    quartile == 5 ~ "C-",
    quartile == 4 ~ "D+",
    quartile == 3 ~ "D",
    quartile == 2 ~ "D-",
    quartile == 1 ~ "F",
  )) -> quartile_data_2002
```


#2003 grading
```{r}
data_2003 <- final_data %>%
  filter(yearDraft == 2003)

column_to_split <- data_2003$player_score

quartiles <- quantile(column_to_split, probs = seq(0, 1, by = 1/12))

quartile_labels <- cut(column_to_split, breaks = quartiles, labels = FALSE, include.lowest = TRUE)

quartile_data <- data_2003 %>%
  select(c(namePlayer, yearDraft, numberPickOverall, player_score))

quartile_data$quartile <- quartile_labels

#Assigning grades to quartiles
quartile_data %>%
  mutate(grade = case_when(
    quartile == 12 ~ "A",
    quartile == 11 ~ "A-",
    quartile == 10 ~ "B+",
    quartile == 9 ~ "B",
    quartile == 8 ~ "B-",
    quartile == 7 ~ "C+",
    quartile == 6 ~ "C",
    quartile == 5 ~ "C-",
    quartile == 4 ~ "D+",
    quartile == 3 ~ "D",
    quartile == 2 ~ "D-",
    quartile == 1 ~ "F",
  )) -> quartile_data_2003
```


#2004 grading
```{r}
data_2004 <- final_data %>%
  filter(yearDraft == 2004)

column_to_split <- data_2004$player_score

quartiles <- quantile(column_to_split, probs = seq(0, 1, by = 1/12))

quartile_labels <- cut(column_to_split, breaks = quartiles, labels = FALSE, include.lowest = TRUE)

quartile_data <- data_2004 %>%
  select(c(namePlayer, yearDraft, numberPickOverall, player_score))

quartile_data$quartile <- quartile_labels

#Assigning grades to quartiles
quartile_data %>%
  mutate(grade = case_when(
    quartile == 12 ~ "A",
    quartile == 11 ~ "A-",
    quartile == 10 ~ "B+",
    quartile == 9 ~ "B",
    quartile == 8 ~ "B-",
    quartile == 7 ~ "C+",
    quartile == 6 ~ "C",
    quartile == 5 ~ "C-",
    quartile == 4 ~ "D+",
    quartile == 3 ~ "D",
    quartile == 2 ~ "D-",
    quartile == 1 ~ "F",
  )) -> quartile_data_2004
```

#2005 grading
```{r}
data_2005 <- final_data %>%
  filter(yearDraft == 2005)

column_to_split <- data_2005$player_score

quartiles <- quantile(column_to_split, probs = seq(0, 1, by = 1/12))

quartile_labels <- cut(column_to_split, breaks = quartiles, labels = FALSE, include.lowest = TRUE)

quartile_data <- data_2005 %>%
  select(c(namePlayer, yearDraft, numberPickOverall, player_score))

quartile_data$quartile <- quartile_labels

#Assigning grades to quartiles
quartile_data %>%
  mutate(grade = case_when(
    quartile == 12 ~ "A",
    quartile == 11 ~ "A-",
    quartile == 10 ~ "B+",
    quartile == 9 ~ "B",
    quartile == 8 ~ "B-",
    quartile == 7 ~ "C+",
    quartile == 6 ~ "C",
    quartile == 5 ~ "C-",
    quartile == 4 ~ "D+",
    quartile == 3 ~ "D",
    quartile == 2 ~ "D-",
    quartile == 1 ~ "F",
  )) -> quartile_data_2005
```

#2006 grading
```{r}
data_2006 <- final_data %>%
  filter(yearDraft == 2006)

column_to_split <- data_2006$player_score

quartiles <- quantile(column_to_split, probs = seq(0, 1, by = 1/12))

quartile_labels <- cut(column_to_split, breaks = quartiles, labels = FALSE, include.lowest = TRUE)

quartile_data <- data_2006 %>%
  select(c(namePlayer, yearDraft, numberPickOverall, player_score))

quartile_data$quartile <- quartile_labels

#Assigning grades to quartiles
quartile_data %>%
  mutate(grade = case_when(
    quartile == 12 ~ "A",
    quartile == 11 ~ "A-",
    quartile == 10 ~ "B+",
    quartile == 9 ~ "B",
    quartile == 8 ~ "B-",
    quartile == 7 ~ "C+",
    quartile == 6 ~ "C",
    quartile == 5 ~ "C-",
    quartile == 4 ~ "D+",
    quartile == 3 ~ "D",
    quartile == 2 ~ "D-",
    quartile == 1 ~ "F",
  )) -> quartile_data_2006
```

#2007 grading
```{r}
data_2007 <- final_data %>%
  filter(yearDraft == 2007)

column_to_split <- data_2007$player_score

quartiles <- quantile(column_to_split, probs = seq(0, 1, by = 1/12))

quartile_labels <- cut(column_to_split, breaks = quartiles, labels = FALSE, include.lowest = TRUE)

quartile_data <- data_2007 %>%
  select(c(namePlayer, yearDraft, numberPickOverall, player_score))

quartile_data$quartile <- quartile_labels

#Assigning grades to quartiles
quartile_data %>%
  mutate(grade = case_when(
    quartile == 12 ~ "A",
    quartile == 11 ~ "A-",
    quartile == 10 ~ "B+",
    quartile == 9 ~ "B",
    quartile == 8 ~ "B-",
    quartile == 7 ~ "C+",
    quartile == 6 ~ "C",
    quartile == 5 ~ "C-",
    quartile == 4 ~ "D+",
    quartile == 3 ~ "D",
    quartile == 2 ~ "D-",
    quartile == 1 ~ "F",
  )) -> quartile_data_2007
```

#2008 grading
```{r}
data_2008 <- final_data %>%
  filter(yearDraft == 2008)

column_to_split <- data_2008$player_score

quartiles <- quantile(column_to_split, probs = seq(0, 1, by = 1/12))

quartile_labels <- cut(column_to_split, breaks = quartiles, labels = FALSE, include.lowest = TRUE)

quartile_data <- data_2008 %>%
  select(c(namePlayer, yearDraft, numberPickOverall, player_score))

quartile_data$quartile <- quartile_labels

#Assigning grades to quartiles
quartile_data %>%
  mutate(grade = case_when(
    quartile == 12 ~ "A",
    quartile == 11 ~ "A-",
    quartile == 10 ~ "B+",
    quartile == 9 ~ "B",
    quartile == 8 ~ "B-",
    quartile == 7 ~ "C+",
    quartile == 6 ~ "C",
    quartile == 5 ~ "C-",
    quartile == 4 ~ "D+",
    quartile == 3 ~ "D",
    quartile == 2 ~ "D-",
    quartile == 1 ~ "F",
  )) -> quartile_data_2008
```

#2009 grading
```{r}
data_2009 <- final_data %>%
  filter(yearDraft == 2009)

column_to_split <- data_2009$player_score

quartiles <- quantile(column_to_split, probs = seq(0, 1, by = 1/12))

quartile_labels <- cut(column_to_split, breaks = quartiles, labels = FALSE, include.lowest = TRUE)

quartile_data <- data_2009 %>%
  select(c(namePlayer, yearDraft, numberPickOverall, player_score))

quartile_data$quartile <- quartile_labels

#Assigning grades to quartiles
quartile_data %>%
  mutate(grade = case_when(
    quartile == 12 ~ "A",
    quartile == 11 ~ "A-",
    quartile == 10 ~ "B+",
    quartile == 9 ~ "B",
    quartile == 8 ~ "B-",
    quartile == 7 ~ "C+",
    quartile == 6 ~ "C",
    quartile == 5 ~ "C-",
    quartile == 4 ~ "D+",
    quartile == 3 ~ "D",
    quartile == 2 ~ "D-",
    quartile == 1 ~ "F",
  )) -> quartile_data_2009
```

#2010 grading
```{r}
data_2010 <- final_data %>%
  filter(yearDraft == 2010)

column_to_split <- data_2010$player_score

quartiles <- quantile(column_to_split, probs = seq(0, 1, by = 1/12))

quartile_labels <- cut(column_to_split, breaks = quartiles, labels = FALSE, include.lowest = TRUE)

quartile_data <- data_2010 %>%
  select(c(namePlayer, yearDraft, numberPickOverall, player_score))

quartile_data$quartile <- quartile_labels

#Assigning grades to quartiles
quartile_data %>%
  mutate(grade = case_when(
    quartile == 12 ~ "A",
    quartile == 11 ~ "A-",
    quartile == 10 ~ "B+",
    quartile == 9 ~ "B",
    quartile == 8 ~ "B-",
    quartile == 7 ~ "C+",
    quartile == 6 ~ "C",
    quartile == 5 ~ "C-",
    quartile == 4 ~ "D+",
    quartile == 3 ~ "D",
    quartile == 2 ~ "D-",
    quartile == 1 ~ "F",
  )) -> quartile_data_2010
```

#2011 grading
```{r}
data_2011 <- final_data %>%
  filter(yearDraft == 2011)

column_to_split <- data_2011$player_score

quartiles <- quantile(column_to_split, probs = seq(0, 1, by = 1/12))

quartile_labels <- cut(column_to_split, breaks = quartiles, labels = FALSE, include.lowest = TRUE)

quartile_data <- data_2011 %>%
  select(c(namePlayer, yearDraft, numberPickOverall, player_score))

quartile_data$quartile <- quartile_labels

#Assigning grades to quartiles
quartile_data %>%
  mutate(grade = case_when(
    quartile == 12 ~ "A",
    quartile == 11 ~ "A-",
    quartile == 10 ~ "B+",
    quartile == 9 ~ "B",
    quartile == 8 ~ "B-",
    quartile == 7 ~ "C+",
    quartile == 6 ~ "C",
    quartile == 5 ~ "C-",
    quartile == 4 ~ "D+",
    quartile == 3 ~ "D",
    quartile == 2 ~ "D-",
    quartile == 1 ~ "F",
  )) -> quartile_data_2011
```

#2012 grading
```{r}
data_2012 <- final_data %>%
  filter(yearDraft == 2012)

column_to_split <- data_2012$player_score

quartiles <- quantile(column_to_split, probs = seq(0, 1, by = 1/12))

quartile_labels <- cut(column_to_split, breaks = quartiles, labels = FALSE, include.lowest = TRUE)

quartile_data <- data_2012 %>%
  select(c(namePlayer, yearDraft, numberPickOverall, player_score))

quartile_data$quartile <- quartile_labels

#Assigning grades to quartiles
quartile_data %>%
  mutate(grade = case_when(
    quartile == 12 ~ "A",
    quartile == 11 ~ "A-",
    quartile == 10 ~ "B+",
    quartile == 9 ~ "B",
    quartile == 8 ~ "B-",
    quartile == 7 ~ "C+",
    quartile == 6 ~ "C",
    quartile == 5 ~ "C-",
    quartile == 4 ~ "D+",
    quartile == 3 ~ "D",
    quartile == 2 ~ "D-",
    quartile == 1 ~ "F",
  )) -> quartile_data_2012
```

#2013 grading
```{r}
data_2013 <- final_data %>%
  filter(yearDraft == 2013)

column_to_split <- data_2013$player_score

quartiles <- quantile(column_to_split, probs = seq(0, 1, by = 1/12))

quartile_labels <- cut(column_to_split, breaks = quartiles, labels = FALSE, include.lowest = TRUE)

quartile_data <- data_2013 %>%
  select(c(namePlayer, yearDraft, numberPickOverall, player_score))

quartile_data$quartile <- quartile_labels

#Assigning grades to quartiles
quartile_data %>%
  mutate(grade = case_when(
    quartile == 12 ~ "A",
    quartile == 11 ~ "A-",
    quartile == 10 ~ "B+",
    quartile == 9 ~ "B",
    quartile == 8 ~ "B-",
    quartile == 7 ~ "C+",
    quartile == 6 ~ "C",
    quartile == 5 ~ "C-",
    quartile == 4 ~ "D+",
    quartile == 3 ~ "D",
    quartile == 2 ~ "D-",
    quartile == 1 ~ "F",
  )) -> quartile_data_2013
```

#2014 grading
```{r}
data_2014 <- final_data %>%
  filter(yearDraft == 2014)

column_to_split <- data_2014$player_score

quartiles <- quantile(column_to_split, probs = seq(0, 1, by = 1/12))

quartile_labels <- cut(column_to_split, breaks = quartiles, labels = FALSE, include.lowest = TRUE)

quartile_data <- data_2014 %>%
  select(c(namePlayer, yearDraft, numberPickOverall, player_score))

quartile_data$quartile <- quartile_labels

#Assigning grades to quartiles
quartile_data %>%
  mutate(grade = case_when(
    quartile == 12 ~ "A",
    quartile == 11 ~ "A-",
    quartile == 10 ~ "B+",
    quartile == 9 ~ "B",
    quartile == 8 ~ "B-",
    quartile == 7 ~ "C+",
    quartile == 6 ~ "C",
    quartile == 5 ~ "C-",
    quartile == 4 ~ "D+",
    quartile == 3 ~ "D",
    quartile == 2 ~ "D-",
    quartile == 1 ~ "F",
  )) -> quartile_data_2014
```

#2015 grading
```{r}
data_2015 <- final_data %>%
  filter(yearDraft == 2015)

column_to_split <- data_2015$player_score

quartiles <- quantile(column_to_split, probs = seq(0, 1, by = 1/12))

quartile_labels <- cut(column_to_split, breaks = quartiles, labels = FALSE, include.lowest = TRUE)

quartile_data <- data_2015 %>%
  select(c(namePlayer, yearDraft, numberPickOverall, player_score))

quartile_data$quartile <- quartile_labels

#Assigning grades to quartiles
quartile_data %>%
  mutate(grade = case_when(
    quartile == 12 ~ "A",
    quartile == 11 ~ "A-",
    quartile == 10 ~ "B+",
    quartile == 9 ~ "B",
    quartile == 8 ~ "B-",
    quartile == 7 ~ "C+",
    quartile == 6 ~ "C",
    quartile == 5 ~ "C-",
    quartile == 4 ~ "D+",
    quartile == 3 ~ "D",
    quartile == 2 ~ "D-",
    quartile == 1 ~ "F",
  )) -> quartile_data_2015
```

#2016 grading
```{r}
data_2016 <- final_data %>%
  filter(yearDraft == 2016)

column_to_split <- data_2016$player_score

quartiles <- quantile(column_to_split, probs = seq(0, 1, by = 1/12))

quartile_labels <- cut(column_to_split, breaks = quartiles, labels = FALSE, include.lowest = TRUE)

quartile_data <- data_2016 %>%
  select(c(namePlayer, yearDraft, numberPickOverall, player_score))

quartile_data$quartile <- quartile_labels

#Assigning grades to quartiles
quartile_data %>%
  mutate(grade = case_when(
    quartile == 12 ~ "A",
    quartile == 11 ~ "A-",
    quartile == 10 ~ "B+",
    quartile == 9 ~ "B",
    quartile == 8 ~ "B-",
    quartile == 7 ~ "C+",
    quartile == 6 ~ "C",
    quartile == 5 ~ "C-",
    quartile == 4 ~ "D+",
    quartile == 3 ~ "D",
    quartile == 2 ~ "D-",
    quartile == 1 ~ "F",
  )) -> quartile_data_2016
```

#Combining Graded Drafts Data
```{r}
complete_graded_data <- bind_rows(quartile_data_2000, quartile_data_2001, quartile_data_2002, quartile_data_2003,
                                  quartile_data_2004, quartile_data_2005, quartile_data_2006, quartile_data_2007,
                                  quartile_data_2008, quartile_data_2009, quartile_data_2010, quartile_data_2011,
                                  quartile_data_2012, quartile_data_2013, quartile_data_2014, quartile_data_2015,
                                  quartile_data_2016)

complete_graded_data$player_score %>% round(2) -> complete_graded_data$player_score
```

#Best and Worst Players Per Class
```{r}
quartile_data_2000 %>%
  arrange(player_score) %>%
  head(1) -> worst_player_2000

quartile_data_2000 %>%
  arrange(desc(player_score)) %>%
  head(1) -> best_player_2000

quartile_data_2001 %>%
  arrange(player_score) %>%
  head(1) -> worst_player_2001

quartile_data_2001 %>%
  arrange(desc(player_score)) %>%
  head(1) -> best_player_2001

quartile_data_2002 %>%
  arrange(player_score) %>%
  head(1) -> worst_player_2002

quartile_data_2002 %>%
  arrange(desc(player_score)) %>%
  head(1) -> best_player_2002

quartile_data_2003 %>%
  arrange(player_score) %>%
  head(1) -> worst_player_2003

quartile_data_2003 %>%
  arrange(desc(player_score)) %>%
  head(1) -> best_player_2003

quartile_data_2004 %>%
  arrange(player_score) %>%
  head(1) -> worst_player_2004

quartile_data_2004 %>%
  arrange(desc(player_score)) %>%
  head(1) -> best_player_2004

quartile_data_2005 %>%
  arrange(player_score) %>%
  head(1) -> worst_player_2005

quartile_data_2005 %>%
  arrange(desc(player_score)) %>%
  head(1) -> best_player_2005

quartile_data_2006 %>%
  arrange(player_score) %>%
  head(1) -> worst_player_2006

quartile_data_2006 %>%
  arrange(desc(player_score)) %>%
  head(1) -> best_player_2006

quartile_data_2007 %>%
  arrange(player_score) %>%
  head(1) -> worst_player_2007

quartile_data_2007 %>%
  arrange(desc(player_score)) %>%
  head(1) -> best_player_2007

quartile_data_2008 %>%
  arrange(player_score) %>%
  head(1) -> worst_player_2008

quartile_data_2008 %>%
  arrange(desc(player_score)) %>%
  head(1) -> best_player_2008

quartile_data_2009 %>%
  arrange(player_score) %>%
  head(1) -> worst_player_2009

quartile_data_2009 %>%
  arrange(desc(player_score)) %>%
  head(1) -> best_player_2009

quartile_data_2010 %>%
  arrange(player_score) %>%
  head(1) -> worst_player_2010

quartile_data_2010 %>%
  arrange(desc(player_score)) %>%
  head(1) -> best_player_2010

quartile_data_2011 %>%
  arrange(player_score) %>%
  head(1) -> worst_player_2011

quartile_data_2011 %>%
  arrange(desc(player_score)) %>%
  head(1) -> best_player_2011

quartile_data_2012 %>%
  arrange(player_score) %>%
  head(1) -> worst_player_2012

quartile_data_2012 %>%
  arrange(desc(player_score)) %>%
  head(1) -> best_player_2012

quartile_data_2013 %>%
  arrange(player_score) %>%
  head(1) -> worst_player_2013

quartile_data_2013 %>%
  arrange(desc(player_score)) %>%
  head(1) -> best_player_2013

quartile_data_2014 %>%
  arrange(player_score) %>%
  head(1) -> worst_player_2014

quartile_data_2014 %>%
  arrange(desc(player_score)) %>%
  head(1) -> best_player_2014

quartile_data_2015 %>%
  arrange(player_score) %>%
  head(1) -> worst_player_2015

quartile_data_2015 %>%
  arrange(desc(player_score)) %>%
  head(1) -> best_player_2015

quartile_data_2016 %>%
  arrange(player_score) %>%
  head(1) -> worst_player_2016

quartile_data_2016 %>%
  arrange(desc(player_score)) %>%
  head(1) -> best_player_2016
```

#Tibble with Best Players
```{r}
best_players <- bind_rows(best_player_2000, best_player_2001,
                          best_player_2002, best_player_2003,
                          best_player_2004, best_player_2005,
                          best_player_2006, best_player_2007,
                          best_player_2008, best_player_2009,
                          best_player_2010, best_player_2011,
                          best_player_2012, best_player_2013,
                          best_player_2014, best_player_2015,
                          best_player_2016)
```

#Tibble with Worst Players
```{r}
worst_players <- bind_rows(worst_player_2000, worst_player_2001,
                          worst_player_2002, worst_player_2003,
                          worst_player_2004, worst_player_2005,
                          worst_player_2006, worst_player_2007,
                          worst_player_2008, worst_player_2009,
                          worst_player_2010, worst_player_2011,
                          worst_player_2012, worst_player_2013,
                          worst_player_2014, worst_player_2015,
                          worst_player_2016)
```

```{r}
ggplot(final_data, aes(x = WS, y = player_score)) +
  geom_point() +
  geom_smooth() +
  labs(title = "Win Shares vs Player Score", x = "Win Shares", y = "Player Score") + 
  theme_bw()
```